\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Prajjwal Mehta}
\newcommand{\yourEmail}{prajjwalmehta75@gmail.com}
\newcommand{\yourPhone}{+91 8851975249}
\newcommand{\githubUserName}{PRAJJWALmehta}
\newcommand{\linkedInUserName}{prajjwalmehta}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{2pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
\educationHeading{Thapar Institute of Engineering and Technology}{B.E. in Computer Science | CGPA: 9.44/10.0}{Patiala, India | 2024}
\sectionsep

%--------------------------------------------------------------
%     Work Experience
%--------------------------------------------------------------
\section{Work Experience}

% --- YOUR CURRENT JOB (MISSING FROM OLD RESUME) ---
% I have added a placeholder here. You MUST fill this with your current work.
\resumeHeading{JP Morgan Chase}{SDE-1}{Bengaluru}{July 2024 - Present}
\begin{bullets}
    \item \textbf{Event-Driven Automation:} Developed the "Auto Task Creation" workflow using a \textbf{Kafka Pub-Sub} model, implementing conditional logic to decouple task generation from the main service.
    \item \textbf{Quality Engineering:} Pioneered the team's first implementation of \textbf{Consumer-Driven Bidirectional Contract Testing}, preventing integration drift between microservices.
    \item \textbf{Observability \& Optimization:} Integrated \textbf{Dynatrace} to monitor service health and executed infrastructure \textbf{Rightsizing} initiatives, reducing cloud resource costs by approx. 15\%.
    \item \textbf{Test Coverage:} Enhanced stability by writing robust test suites using \textbf{SmartSpec} and successfully executed spring boot upgrades
\end{bullets}
\sectionsep

% --- YOUR INTERNSHIP (REWRITTEN FOR IMPACT) ---
\resumeHeading{JP Morgan \& Chase}{Summer Analyst Intern}{Bengaluru}{Jun 2023 - July 2023}
\begin{bullets}
    \item \textbf{High-Performance API:} Engineered a Data Fetching Service using \textbf{GraphQL} and \textbf{Directed Acyclic Graphs (DAGs)}.
    \item \textbf{98\% Latency Reduction:} Implemented node-level caching strategies, slashing complex query execution time from \textbf{900ms to 10ms}.
    \item \textbf{Tooling:} Built an internal debugging dashboard that aggregates data from internal/external DBs, reducing root-cause analysis time for the team.
\end{bullets}
\sectionsep

% --- CLUB LEADERSHIP (REBRANDED) ---
\resumeHeading{Entrepreneurship Development Cell}{Tech Lead & Design Head}{Thapar University}{2022 - 2024}
\begin{bullets}
    \item Led the digital presence for "Pitchverse," managing web assets and reducing page load speeds through image optimization.
    \item Managed a team of 5 designers/developers to deliver marketing assets under strict deadlines.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Key Projects}

% --- Project 1: Focus on the "System" aspect of E-commerce ---
\projectHeading{E-Commerce Backend \& Payments}{https://github.com/PRAJJWALmehta/WebDev}{MERN Stack, Stripe API, Redis}
\begin{bullets}
    \item Designed a scalable e-commerce architecture supporting secure payments via Stripe integration.
    \item Implemented \textbf{JWT Authentication} and role-based access control (Admin vs User) to secure API endpoints.
    \item \textbf{Database Design:} Normalized MongoDB schemas to handle inventory and order history efficiently.
\end{bullets}
\sectionsep

% --- Project 2: Make ML sound like Engineering ---
\projectHeading{Covid-19 X-Ray Pipeline}{https://github.com/PRAJJWALmehta/Machine-Learning-}{Python, PyTorch, ResNet-18}
\begin{bullets}
    \item Built an automated image classification pipeline achieving \textbf{XX\% accuracy} on test data.
    \item Processed and augmented a dataset of [Number] images to prevent overfitting and improve model generalization.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Technical Skills}
\begin{skillList}
    \singleItem{Languages:}{Java, C++, JavaScript (ES6+), Python, SQL}
    \\
    \singleItem{Frameworks:}{Spring Boot, React.js, Node.js, Express, NextJS, GraphQL}
    \\
    \singleItem{Infrastructure:}{Git, Docker, AWS (Basics), MongoDB, PostgreSQL}
    \\
    \singleItem{Concepts:}{Data Structures, Algorithms, OOP, REST APIs, System Design Basics}
\end{skillList}

\end{document}
